---
title: "p8105_hw1_lcc2181"
author: "Lauren Cohen"
date: "9/22/2021"
output: github_document
---

## Problem 1

Loading the tidyverse

```{r}
library(tidyverse)
```

Creating the data frame. Using 'set.seed' to ensure reproducibility.

```{r}
set.seed(1)

prob1_df = tibble (
  norm_samp = rnorm(10),
  norm_samp_pos = norm_samp > 0,
  vec_char = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  vec_factor = factor(c("high", "high", "high", "medium", "medium", "medium", "low", "low", "low", "low"))
)

prob1_df
```

Taking the mean of each variable in the data frame.

```{r}
mean(pull(prob1_df,norm_samp))
mean(pull(prob1_df,norm_samp_pos))
mean(pull(prob1_df,vec_char))
mean(pull(prob1_df,vec_factor))
```
Taking the mean of norm_samp and norm_samp_pos works. Taking the mean of vec_char and vec_factor did not work. When attempting to take the mean of vec_char and vec_factor, it returned "NA" with a warning message stating that the argument is not numeric or logical.

The following code chunk applies the 'as.numeric' function to the logical, character, and factor variables.

```{r, results='hide'}
as.numeric(pull(prob1_df,norm_samp_pos))
as.numeric(pull(prob1_df,vec_char))
as.numeric(pull(prob1_df,vec_factor))
```
For norm_samp_pos (the logical vector), all values are assigned as 0. 
For vec_char (the character vector), all values are assigned "NA". 
For vec_factor (the factor vector), the different levels are assigned numerical values of 1, 3, and 2.

## Problem 2

The package containing penguins was installed directly in the console.

The following code loads in the penguins dataset.

```{r}
data("penguins", package = "palmerpenguins")
```

The names of the variables in this data set are: `r names(penguins)`

The number of rows in the data set is: `r nrow(penguins)`
The number of columns in the data set is: `r ncol(penguins)`

The mean flipper length is: `r mean(pull(penguins, flipper_length_mm), na.rm=TRUE)`

The code chunk below creates a scatter plot of flipper length vs. bill length. Points are colored by species. The scatter plot is exported to the project directory.

```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("penguin_scatter_plot.pdf", height=4, width =6)
```

